### 2023-09-22 sections/summary.tex
Update summary.tex

\textcolor{black}{My doctoral research is supervised by Professor Petra Schleiter and focuses on the causes and consequences of ministerial turnover in 12 Latin American presidential countries from the mid-1970s to date. My project integrates elements of the principal-agent theory to evaluate specific incentives and strategies of the actors in presidential systems, considering the regime’s institutional features. In my data-gathering process, I applied optical character recognition (OCR), natural language processing (NLP) and machine learning techniques to almost 50 years of press report archives. In addition, my empirical strategy employs propensity score matching methods, semiparametric competing risks models and instrumental-variable regressions.}

>>>>

\textcolor{black}{My doctoral research is supervised by Professor Petra Schleiter and focuses on the causes and consequences of ministerial turnover in 12 Latin American presidential countries from the mid-1970s to date. My project integrates elements of the principal-agent theory to evaluate specific incentives and strategies of the actors in presidential systems, considering the regime’s institutional features. In my data-gathering process, I applied optical character recognition (OCR), natural language processing (NLP) and machine learning techniques to almost 50 years of press report archives. In addition, my empirical strategy employs propensity score matching methods, semiparametric competing risks models and instrumental variables (IV) regressions.}
